\section{Future Work}
\label{sec:future_work}

\subsection{Things to add}

At time of writing, it doesn't feel like there are many particularly pressing missing features,
save one. I found at the end of my 3rd year project that getting a word count was much more
painful than it needed to be, since I discovered that figure captions are not included in the
built-in OverLeaf wordcount. I ended up taking the PDF produced by my \LaTeX\ and copying any text
to be included into a Word document. I then took the count that I got from that document over to
my \LaTeX\ to be re-rendered. I looked briefly for a word count library, but could find
surprisingly few packages that seemed to offer a word count, and none that I noticed were suitably
configurable to make the word count usable. If there is one you're familiar with, please read on!

For a current list of missing features and required bug fixes, please see the
\href{https://github.com/Ned-Stevenson/OxCSProject/issues}{GitHub issues page}.

\subsection{How to contribute}

If you feel that there are any features that need be added or changes to be made, please go to the
GitHub repository where you got this template and add an issue for it. And if you feel like trying
out working on open source projects, consider picking an issue and implementing it as I describe
below.

If you do want to do the work that resolving an issue would require, then make a fork of
OxCSProject in the same way as described in Section~\ref{sec:installation}. From there, you can
make whichever changes and write in whichever features you'd like. To make them available for all
to enjoy, you can then create a pull request to merge those improvements back into the template
for the next generation of Oxford Computer Scientists. This is the same process as contributing to
pretty much any open source project, and something worth trying at least once.
